\documentclass[11pt, leqno, oneside]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{float}

\usepackage[a4paper, margin=1in]{geometry}

\usepackage[backend=bibtex, sortcites=true, style=numeric-comp, sorting=none]{biblatex}

\title{Performance test assigment}
\author{Name: Bence Nagy\\Neptun code: HVTDD4}
\date{}

\begin{document}

\maketitle

\section{Test setup}

The laptop I used for testing is a M3 Macbook Air running macOS 26.2.
For creating the test plans and perfoming the perfomance tests I have used Apache JMeter.

\section{Test Plan}
The System Under Test I decided to use for my tests was a sample test website provided by BlazeMeter: https://blazedemo.com/.
In my tests I have targeted the homepage, the reserve page and the purchase page. The URLs for the pages are the following:
\begin{itemize}
  \item Homepage: https://blazedemo.com/index.php
  \item Reserve page: https://blazedemo.com/reserve.php
  \item Purchase page: https://blazedemo.com/purchase.php
\end{itemize}


\section{Types of tests conducted}

The site was tested with three distintive types of perfomance tests:

\vspace{12pt}
{\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{|X|X|}
  \hline
  \textbf{Type} & \textbf{Description} \\
  \hline
  Baseline stress test & Number of threads (users) : 2 \newline Ramp-up period: 2 seconds \newline Loop count: 10 \\
  \hline
  Stress test & Number of threads (users) : 20 \newline Ramp-up period: 2 seconds \newline Loop count: 10 \\
  \hline
  Spike test & Number of threads (users) : 200 \newline Ramp-up period: 1 seconds \newline Loop count: 5 \\
  \hline
\end{tabularx}}

\section{Initial Expectations}

Before running the tests I expected the site to respond within 500 - 1000 milliseconds during the baseline perfomance test. I also expected the stress test, and spike tests both to cause about a 100 milliseconds increase in the median response times.

\section{Results}

The results gathered during the tests are the following including the number of samples, minimum response times, maximum response time, average response time, median response time (in milliseconds), and the error rate.
The results are given for each of the requests and the aggregate total.

\subsection{Baseline test}

\begin{table}[H]
\centering
\small
\begin{tabularx}{\textwidth}{X r r r r r r}
  \hline
  \textbf{Request} & \textbf{\# Samples} & \textbf{Min (ms)} & \textbf{Max (ms)} & \textbf{Avg (ms)} & \textbf{Median (ms)} & \textbf{Error \%} \\
  \hline
  Homepage      & 20 & 361 & 725 & 415 & 396 & 0.00\% \\
  Reserve Page  & 20 & 369 & 552 & 404 & 398 & 0.00\% \\
  Purchase Page & 20 & 377 & 498 & 404 & 392 & 0.00\% \\
  \hline
  \textbf{Total} & \textbf{60} & \textbf{361} & \textbf{725} & \textbf{408} & \textbf{397} & \textbf{0.00\%} \\
  \hline
\end{tabularx}
\caption{Baseline perfomance test results}
\label{tab:performance}
\end{table}

\subsection{Stress test}

\begin{table}[H]
\centering
\small
\begin{tabularx}{\textwidth}{X r r r r r r}
  \hline
  \textbf{Request} & \textbf{\# Samples} & \textbf{Min (ms)} & \textbf{Max (ms)} & \textbf{Avg (ms)} & \textbf{Median (ms)} & \textbf{Error \%} \\
  \hline
  Homepage      & 200 & 353 & 727 & 410 & 392 & 0.00\% \\
  Reserve Page  & 200 & 358 & 547 & 399 & 392 & 0.00\% \\
  Purchase Page & 200 & 363 & 529 & 405 & 398 & 0.00\% \\
  \hline
  \textbf{Total} & \textbf{600} & \textbf{353} & \textbf{727} & \textbf{405} & \textbf{393} & \textbf{0.00\%} \\
  \hline
\end{tabularx}
\caption{Stress perfomance test results}
\label{tab:stress}
\end{table}

\subsection{Spike test}

\begin{table}[H]
\centering
\small
\begin{tabularx}{\textwidth}{X r r r r r r}
  \hline
  \textbf{Request} & \textbf{\# Samples} & \textbf{Min (ms)} & \textbf{Max (ms)} & \textbf{Avg (ms)} & \textbf{Median (ms)} & \textbf{Error \%} \\
  \hline
  Homepage      & 1000 & 362 & 1813 & 639 & 550 & 0.00\% \\
  Reserve Page  & 1000 & 355 & 1767 & 635 & 521 & 0.00\% \\
  Purchase Page & 1000 & 360 & 1850 & 631 & 522 & 0.00\% \\
  \hline
  \textbf{Total} & \textbf{3000} & \textbf{355} & \textbf{1850} & \textbf{635} & \textbf{530} & \textbf{0.00\%} \\
  \hline
\end{tabularx}
\caption{Spike perfomance test results}
\label{tab:spike}
\end{table}


\section{Conclusion}
As we can see in the results, the System Under Test seemed the respond during the baseline perfomance tests close to the expected response times.
The stress test produced similar results to our baseline tests, which goes against what I anticipated initially.

However, the spike test produced slower response times compared to the baseline perfomance test (as expected).
The median response time between the spike test and the baseline was 133 milliseconds.
Also, the average response time was 105 milliseconds higher than the median response time in the spike test, which seems to indicate that in the measurements we had a few slower response times.
This is also supported by the fact that we witnessed a 1850 millisecond maximum response time during the spike perfomance test. 

Also notably, the System Under Test hasn't produced any errors throughout the 3 tests as we had a 0.00\% error rate in all of the tests.

\end{document}